---
title: "Untitled"
author: "STAT613_HW_Scraping&Rectangling"
date: "3/19/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(rvest)
library(dplyr)
library(tidyverse)
library(repurrrsive)
listviewer::jsonedit(gh_users)
```

#Ques 1):
```{r}
Link <- "https://www.imdb.com/list/ls091520106/"
page = read_html(Link)
Title = page%>% html_nodes(".lister-item-header a")%>%
  html_text()
Title
```

```{r}
Link <- "https://www.imdb.com/list/ls091520106/"
page = read_html(Link)
Ratings = page%>% html_nodes(".ipl-rating-star.small .ipl-rating-star__rating")%>%
  html_text()
Ratings
```

```{r}
Link <- "https://www.imdb.com/list/ls091520106/"
page = read_html(Link)
Runtime = page%>% html_nodes(".runtime")%>%
  html_text()
Runtime
```
#Converting Ratings as.numeric: 
```{r}
Ratings<- as.numeric(Ratings)
```

```{r}
moviesdataframe = data.frame(Title,Ratings,Runtime)
moviesdataframe
```
#Checking if it a tibble: 
```{r}
is_tibble(moviesdataframe)
```

```{r}
as_tibble(moviesdataframe)
```


#Ques 2): 
#a): 
#Nested list typically is a list within a list, may be 
#ordered or unordered. 
#The objects/components within the list do not have 
#to be of the same family (can be different types) e.g. 
#integer, double, character string or even
#a list (called nested list) within the original list.  

#b): 
#Raw data/information is given (without any
#particular structure or order), information on all 
#activities conducted for each of the 6 Git Hub Repositories:
#E.g: urls on notifications, pull requests, fork, commits, 
#profile id, name, homepage, subscriptions, issues etc.
```{r}
gh_repos
```

#c): 
#This will add structure and improvement to the data. 
#The information will now be displayed in a concise, more
#organized format rather than being spread out. 
#We now see 6 listed repos, each with components of 
#30 and one with 26 subsets. However, the components cannot
#be retrieved here.  
```{r}
repos <- tibble(repo = gh_repos)
repos
```

#d): 
#The following code now displays an array for each of
#6 Repos, the subset data(characteristics) for each Repos, 
#can now be retrieved by clicking the arrow. 
#Each of the 6 arrows contain 30 and 26 subsets which 
#further contain 68 elements of detailed data e.g. id etc.  
```{r}
listviewer::jsonedit(gh_repos)
```


#e):
```{r}
tibble(repo = gh_repos)%>%
  unnest_auto(repo)%>%
  unnest_auto(repo) -> new
new
```


